
```{r}
#this package is R native
library(lattice)
```
Boxplot
```{r}
bwplot(trees$Volume)
bwplot(trees$Volume, main="trees",xlab="Volume")
```
Histogram 
aspect is proportion, nint number of sectors, type: percent, count, density
```{r}
histogram(trees$Volume, main="trees",xlab="Volume",aspect=1, type = "percent", nint=5 )
```
Conditional histogram
```{r}
#chicken weight re
chickwts
#histogram
histogram(chickwts$weight)
#data aggregation
aggregate(chickwts$weight, by=list(chickwts$feed), FUN=sum)
#conditional histogram
histogram( ~weight | feed, data=chickwts)
```
conditional histogram chart
CO2, six trees in two places, chilled or not during  the night
```{r}
#CO2, conc: CO2 concentration, uptake: CO2 capture 
CO2
xyplot(CO2$conc ~  CO2$uptake)
#type is the origin
xyplot(CO2$conc ~  CO2$uptake | CO2$Type)
#regrigerado ou não
xyplot(CO2$conc ~  CO2$uptake | CO2$Treatment)
```
esophageal cancer
agegp: age, alcgp: alcool, tobgp: tabaco
```{r}
esoph
dotplot(esoph$alcgp ~ esoph$ncontrols, data=esoph)
dotplot(esoph$alcgp ~ esoph$ncontrols | esoph$tobgp)
```
Dispersion matrix
```{r}
splom(~CO2[4:5] | CO2$Type, CO2)
```
conditional density
```{r}
densityplot(~CO2$conc | CO2$Treatment, plot.points=FALSE)
densityplot(CO2$conc)
densityplot(~CO2$conc | CO2$Treatment)
```
3d chart
Spray to repel bees
```{r}
OrchardSprays
cloud(decrease ~  rowpos * colpos, data=OrchardSprays)
cloud(decrease ~  rowpos * colpos, groups=treatment, data=OrchardSprays)
```
Level plot
Girth, hieght e volume of trees
```{r}
trees
levelplot(Girth ~ Height * Volume, data=trees)
```

