cars with MPG and other aspects 
mpg, hp, cyl, disp
```{r}
#install.packages("corrgram")
library(corrgram)
mtcars
dim(mtcars)
```
Correlation
```{r}
cor(mtcars[1:4])
corrgram(mtcars[1:4], order=TRUE, lower.panel=panel.shade,
         upper.panel=panel.pie, text.panel=panel.txt,
         main="cars")
```
analyzing cyl vs mpg
```{r}
plot(mtcars$mpg ~ mtcars$disp, ylab="mpg", xlab="cyl", main="cars")
```
model using cyl to predict mpg
Intercept and angle
```{r}
modelo = lm(mpg ~ disp, data=mtcars)
modelo
```
Determination coefficient (71% of the dependent variable is explained by the explanatory variable)
R2 adjusted
```{r}
summary(modelo)$r.squared 
summary(modelo)$adj.r.squared
```
chart with line model
```{r}
#use with Crtrl+ Shif + Enter
plot(mpg ~ disp, data=mtcars,ylab="mpg", xlab="cyl", main="cars")
abline(modelo)
```
predicting mpg com 200 cyl
```{r}
predict(modelo,data.frame(disp = 200))
```
adding two independent variables hp and cyl
```{r}
modelo = lm(mpg ~ disp +  hp + cyl, data=mtcars)
modelo
```
Determination coefficient (71% of the dependent variable is explained by the explanatory variable)
R2 adjusted
```{r}
summary(modelo)$r.squared 
summary(modelo)$adj.r.squared
```
Predicting mpg with 200 cyl, 100 hp and 4 cyl
```{r}
predict(modelo,data.frame(disp = 200, hp=100, cyl=4))
```
